
---
title: "About the luckyModel package"
author: "Weibin Huang"
date: "`r Sys.Date()`"
output:
  md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# luckyModel

<p align="left">
<a href=""><img src="https://img.shields.io/github/r-package/v/huangwb8/luckyModel"></a>
<a href="https://github.com/huangwb8/luckyModel/blob/master/license.txt"><img src="https://img.shields.io/badge/license-MIT-green"></a>
<a href=""><img src="https://img.shields.io/badge/platform-windows%20%7C%20linux-lightgrey"></a>
<a href=""><img src="https://img.shields.io/github/commit-activity/m/huangwb8/luckyModel"></a>
<a href=""><img src="https://img.shields.io/github/stars/huangwb8/luckyModel?style=social"></a>
<a href="https://github.com/huangwb8/luckyModel/issues"><img src="https://img.shields.io/github/issues-raw/huangwb8/luckyModel"></a>
</p>

###  Bioinformatic model of third-party lucky series packages

Model ensemble for third-party lucky series, such [**GSClassifier**](https://github.com/huangwb8/GSClassifier)

## :alien: Authors

Weibin Huang (黄伟斌);  <654751191@qq.com>

1. Guangdong Provincial Key Laboratory of Digestive Cancer Research, The Seventh Affiliated Hospital of Sun Yat-sen University, No. 628 Zhenyuan Road, Shenzhen, 518107, Guangdong, People’s Republic of China. Digestive Diseases Center

2. Department of Gastrointestinal Surgery, the First Affiliated Hospital of Sun Yat-sen University, 58 Zhongshan 2nd Road, Guangzhou 510080, Guangdong, People’s Republic of China.

## :+1: Installaton

```{R}
# Install "devtools" package
if (!requireNamespace("devtools", quietly = TRUE))
    install.packages("devtools")
    
# Install luckyModel
if (!requireNamespace("luckyModel", quietly = TRUE))
    devtools::install_github("huangwb8/luckyModel")
```

## :seedling: Usage

Load the pacakge
```{r}
library(luckyModel)

```


Which projects were supported in `luckyModel`?

```{r}
list_project()
```

Explore models in a project, just:

```{R}
list_model(project='GSClassifier')
```

Calling a specific model, just:

```{r, warning=FALSE}
model <- lucky_model(project = 'GSClassifier',
                    developer='HWB',
                    model = 'PAD',
                    version = 'v20200110')
names(model)
```


